
### ozbabynames 

This dataset contains summary data for popular Australian baby names by sex, state and year. 

```{r, eval = FALSE}
#devtools::install_github("ropenscilabs/ozbabynames")
```

```{r, eval = TRUE}
library(ozbabynames)
str(ozbabynames)
```

This dataset was created at rOpenSci OzUnconf 2019. Repo: [ozbabynames](https://github.com/ropenscilabs/ozbabynames)


### eechidna

This package contains datasets from the Australian Federal elections in 2001, 2004, 2007, 2010, 2013 and 2016, along with the Australian Census information for each House of Representatives electorate from the 2001, 2006, 2011 and 2016 Censuses. Additionally, Census information is imputed for electorates in years 2004, 2007, 2010 and 2013.

```{r, eval=FALSE}
devtools::install_github("ropenscilabs/eechidna")
```

#### Australian Federal Elections Datasets

```{r, eval = TRUE}
str(eechidna::fp01)
str(eechidna::fp04)
str(eechidna::fp07)
str(eechidna::fp10)
str(eechidna::fp13)
str(eechidna::fp16)

```

#### Australian Federal Elections Datasets

```{r, eval = TRUE}
str(eechidna::abs2001)
str(eechidna::abs2004)
str(eechidna::abs2007)
str(eechidna::abs2010)
str(eechidna::abs2013)
str(eechidna::abs2016)

```


These datasets were created at rOpenSci auunconf 2016. Repo: [eechidna](https://github.com/ropenscilabs/eechidna)


### ozmacrodata

Functions to search and download Australian economics dataset. 

```{r, eval = FALSE}
devtools::install_github("AU-burgr/ozdata")
```

```{r, eval = FALSE}
library(ozdata)
```

#### Examples 

To download data from [](http://ausmacrodata.org), you can search the website and return a table of available datasets. You then download the data of interest. 

```{r, eval = FALSE}
macro_datasets <- search_ausmacrodata('births')
macro_datasets
```

This dataset was created at BURGr R Unconf 2017. Repo: [ozdata](https://github.com/AU-BURGr/ozdata)


### datagovau

Here we provide tools to programmatically import and explore Australian data sets. Data can be obtained from the official Australian government portal, which catalogues over 40,000 data sets (https://data.gov.au).

```{r, eval = FALSE}
devtools::install_github("ropenscilabs/datagovau/pkg")

```

#### Example

```{r, eval = TRUE}
library(dplyr)
library(datagovau)

# download details of datasets with 'water' in their name:
res <- search_data("name:water", limit = 20)

# download the datasets in the second pacakge listed their:
water_data <- res %>% filter(can_use == "yes") %>% slice(1) %>% get_data

# look at the first rectangle of data (at time of writing there were four such rectangles)
head(water_data[[1]])
```

Check out [this README file](https://github.com/ropenscilabs/datagovau) on Github for more information. 


### HILDA

The Household, Income and Labour Dynamics in Australia (HILDA) Survey is a household-based panel study that collects valuable information about economic and personal well-being, labour market dynamics and family life. It aims to tell the stories of the same group of Australians over the course of their lives. It was instrumental in illustrating an increase in births due to the Baby Bonus. [More information can be found here](https://melbourneinstitute.unimelb.edu.au/__data/assets/pdf_file/0010/2437426/HILDA-SR-med-res.pdf). 

Apply to access the data [here](https://melbourneinstitute.unimelb.edu.au/hilda/for-data-users)


### Austats

This package allows researchers to quickly search and download selected Australian Bureau of Statistics (ABS) and Reserve Bank of Australia (RBA) data in a programmatic and reproducible fashion. 

```{r, eval = FALSE}
install.packages("raustats")
```

```{r, eval = FALSE}
library(raustats)
```

#### Example

You can download Australian Bureau of Statistics data using the catalogue numbers. 

```{r, eval = FALSE}
#Download a whole ABS document
cpi_all <- abs_cat_stats("6401.0")
str(cpi_all)

#Download a single sheet
cpi <- abs_cat_stats("6401.0", tables="Table.+1\\D")
```

** NOTE: currently not working though an issue has been ** 

Checkout the vignette for how to [download datasets within R](https://cran.r-project.org/web/packages/raustats/vignettes/raustats_introduction.html)


### LSAC

The Longitudinal Study of Australian Children data is available, pending completion of confidentiality and data access. [See here](https://www.dss.gov.au/about-the-department/publications-articles/research-publications/longitudinal-data-initiatives/footprints-in-time-the-longitudinal-study-of-indigenous-children-lsic/growing-up-in-australia-the-longitudinal-study-of-australian-children-lsac) for more information.


### Marriage Equality Data

Data from the Australian Bureau of Statistics from the 2017 Marriage Equality Postal Survey [can be downloaded here](https://www.abs.gov.au/ausstats/ABS@Archive.nsf/log?openagent&australian_marriage_law_postal_survey_2017_-_participation_final.xls&1800.0&Time%20Series%20Spreadsheet&830FD42482B309D6CA2581F0001A085B&0&2017&11.12.2017&Latest) [response data](https://www.abs.gov.au/ausstats/ABS@Archive.nsf/log?openagent&australian_marriage_law_postal_survey_2017_-_response_final.xls&1800.0&Time%20Series%20Spreadsheet&916379DAEE6E960CCA2581F0001A08A9&0&2017&11.12.2017&Latest).


### Footprints in Time: LSIC

The Longitudinal Study of Indigenous Children (LSIC) aims to improve understanding of the issues faced by Aboriginal and Torres Strait Islander children, their families and communities. Data access can be requested through the [website](ttps://www.dss.gov.au/about-the-department/national-centre-for-longitudinal-studies/overview-of-footprints-in-time-the-longitudinal-study-of-indigenous-children-lsic).


### Convict Indexes

Between 1788 and 1842 about 80,000 convicts were transported to New South Wales. Of these, about 85% were men and 15% were women. Almost two thirds of convicts were English (along with a small number of Scottish and Welsh), with the Irish making up the remaining one third.

Convicts were usually given sentences of transportation for seven, 14 years or life. Some convicts in the 1830s received ten-year sentences. About one quarter of the convicts were sentenced to ‘the term of their natural lives’, and a proportion of these had reprieves from the death sentence.

There are seven indexes containing around 140,000 entries in total, which can be accessed through the [website](https://data.gov.au/dataset/ds-nsw-acdd01d0-d700-465c-a183-735c4f139ca0/details).

### Indigenous Mortality

Indigenous mortality data from the [indmortality package](https://github.com/robjhyndman/indmortality).

### Australian Demographic Data Base

Demographic database from the [addb package](https://github.com/robjhyndman/addb).
