
### ozbabynames 

This dataset contains summary data for popular Australian baby names by sex, state and year. 

```{r, eval = FALSE}
#devtools::install_github("ropenscilabs/ozbabynames")
```

```{r, eval = TRUE}
library(ozbabynames)
str(ozbabynames)
```

This dataset was created at rOpenSci OzUnconf 2019. Repo: [ozbabynames](https://github.com/ropenscilabs/ozbabynames)


### eechidna

This package contains datasets from the Australian Federal elections in 2001, 2004, 2007, 2010, 2013 and 2016, along with the Australian Census information for each House of Representatives electorate from the 2001, 2006, 2011 and 2016 Censuses. Additionally, Census information is imputed for electorates in years 2004, 2007, 2010 and 2013.

```{r, eval=FALSE}
devtools::install_github("ropenscilabs/eechidna")
```

#### Australian Federal Elections Datasets

```{r, eval = TRUE}
str(eechidna::fp01)
str(eechidna::fp04)
str(eechidna::fp07)
str(eechidna::fp10)
str(eechidna::fp13)
str(eechidna::fp16)

```

#### Australian Federal Elections Datasets

```{r, eval = TRUE}
str(eechidna::abs2001)
str(eechidna::abs2004)
str(eechidna::abs2007)
str(eechidna::abs2010)
str(eechidna::abs2013)
str(eechidna::abs2016)

```


This dataset was created at rOpenSci auunconf 2016. Repo: [eechidna](https://github.com/ropenscilabs/eechidna)


### ozmacrodata

Aus economics dataset. 

```{r, eval=TRUE}
#devtools::install_github("AU-burgr/ozdata")
library(ozdata)

```


This dataset was created at BURGr R Unconf 2017. Repo: [ozdata](https://github.com/AU-BURGr/ozdata)
