---
title: "OZdatasets"
author: "Kristy Robledo, Jessica Lee, Alyce Russell, Tania Prvan"
date: "12/12/2019"
output: 
  html_document:
    theme: readable
    highlight: monochrome
    toc: TRUE
    toc_float: TRUE
    includes:
      in_header: './images/ropensci_logo.svg'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE )
```

This repository was compiled at the rOpenSci OzUnconf19 @ University of Sydney, December 2019. 

Its purpose is to document datasets previously created at OzUnconf events, as well as other interesting and unique Australian datasets and resources. We have made our best attempt to have these links/packages functioning. However, in the case of errors still existing, an issue has been logged on Github. 

## Summary table
```{r, echo = FALSE}
library(DT)
df<-rbind(c("ozflights", "transport", "package", "Flight data"),
          c("ozroaddeaths", "transport", "package", "Road deaths"),
          c("vehicles", "transport", "link", "Vehicle use"),
          c("beaches", "environment", "link", "Sydney beach data"),
          c("river", "environment", "link", "River and rainfall data"),
          c("birds", "environment", "link", "Data about Australian birds"),
          c("atlas", "environment", "link", "Atlas of Australian biodiversity"),
          c("fires", "environment", "link", "Bush fire data"),
          c("ozbabynames", "demographics", "package", "Baby names in Australia"),
          c("eechidna", "demographics", "package", "Election and census data"),
          c("ozdata", "demographics", "package", "Australian economic data"),
          c("raustats", "demographics", "package-BROKEN??", "Household survey"),
          c("longitudinal", "demographics", "link", "Longitudinal"),
          c("marriageequality", "demographics", "link", "Data from the 2017 marriage equality survey"),
          c("aflinfo", "sport", "package", "AFL data"),
          c("fitzRoy", "sport", "package", "AFL data"),
          c("cricketdata", "sport", "package", "Cricket data"),
          c("ozmaps", "maps", "package", "Maps of Australia"),
          c("ozdates", "misc", "package", "Maps of Australia"),
          c("smokeybear", "", "package", ""), # TO ADD
          c("learningtower", "", "package", "") # TO ADD
)

DT::datatable(df, colnames = c("Name","Topic","Package/Link","Data explanation"))

```

## Transport 

```{r child="transport.Rmd"}
```

## Environmental

```{r child="enviro.Rmd"}
```

## Demographics

```{r child="demo.Rmd"}
```

## Sport

```{r child="sport.Rmd"}
```

## Maps

The [readme file](https://github.com/mdsumner/ozmaps/) is very descriptive for how to create Maps of australia in ggplot. 

```{r, eval = FALSE}
install.packages("ozmaps")
```

```{r, eval = TRUE}
library(ozmaps)

```

## Miscellaneous 

### Ozdates

Important australian dates, like public holidays, in a downloadable file. The README is on [github](https://deanmarchiori.github.io/ozdates/) explains how to use. 

```{r, eval=FALSE}
devtools::install_github("deanmarchiori/ozdates")
```


