---
title: "OZdatasets"
author: "Kristy Robledo, Jessica Lee, Alyce Russell, Tania Prvan"
date: "12/12/2019"
output: 
  html_document:
    keep_md: TRUE 
    theme: spacelab
    highlight: monochrome
    toc: TRUE
    toc_float: TRUE
---

<div style="margin-bottom:50px;">

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"./images/ropensci_logo.svg\" style=\"position:absolute; top:0; right:0; padding:20px; height:150px\"></div>');
  $('#header').css('margin-right', '120px')
});
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE )
```

</div>

This repository was compiled at the rOpenSci OzUnconf19 @ University of Sydney, December 2019. 

Its purpose is to document datasets previously created at OzUnconf events, as well as other interesting and unique Australian datasets and resources. We have made our best attempt to have these links/packages functioning. However, in the case of errors still existing, an issue has been logged on Github. 

<div style="margin-bottom:50px;">
</div>

## Summary table
```{r, echo = FALSE}
library(DT)
df<-rbind(c("ozflights", "transport", "package", "Flight data"),
          c("ozroaddeaths", "transport", "package", "Road deaths"),
          c("vehicles", "transport", "link", "Vehicle use"),
          c("beaches", "environment", "link", "Sydney beach data"),
          c("river", "environment", "link", "River and rainfall data"),
          c("birds", "environment", "link", "Data about Australian birds"),
          c("atlas", "environment", "link", "Atlas of Australian biodiversity"),
          c("fires", "environment", "link", "Bush fire data"),
          c("bomrang", "environment", "package", "access to BOM data"), 
          c("QOL enviro", "environment", "links", "links to QLD environment and Maps data"), 
          c("CSIRO data", "environment", "links", "CSIRO data portal, some behind confidentiality"),
          c("Ocean data", "environment", "links", "Australian ocean data network"), 
          c("DataVic", "environment", "links", "Access to enironmental and non environmental data from DataVic"),
          
          c("ozbabynames", "demographics", "package", "Baby names in Australia"),
          c("eechidna", "demographics", "package", "Election and census data"),
          c("ozdata", "demographics", "package", "Australian economic data"),
          c("raustats", "demographics", "package-BROKEN??", "Household survey"),
          c("longitudinal", "demographics", "link", "Longitudinal"),
          c("marriageequality", "demographics", "link", "Data from the 2017 marriage equality survey"),
          c("aflinfo", "sport", "package", "AFL data"),
          c("fitzRoy", "sport", "package", "AFL data"),
          c("cricketdata", "sport", "package", "Cricket data"),
          c("ozmaps", "maps", "package", "Maps of Australia"),
          c("ozdates", "misc", "package", "Maps of Australia"),
          c("smokeybear", "", "package", ""), # TO ADD
          c("learningtower", "", "package", ""), # TO ADD
          c("hackerspace", "misc", "links", "Access to data from hackerspace projects")
)

DT::datatable(df, colnames = c("Name","Topic","Package/Link","Data explanation"), 
              options = list(
                pageLength = 20,
                lengthMenu = c(10, 20, 50)
              )
)

```

<div style="margin-bottom:50px;">
</div>

## Transport 

```{r child="transport.Rmd"}
```

<div style="margin-bottom:50px;">
</div>

## Environmental

```{r child="enviro.Rmd"}
```

<div style="margin-bottom:50px;">
</div>

## Demographics

```{r child="demo.Rmd"}
```

<div style="margin-bottom:50px;">
</div>

## Sport

```{r child="sport.Rmd"}
```

<div style="margin-bottom:50px;">
</div>


## Miscellaneous 

### ozmaps

The [README file](https://github.com/mdsumner/ozmaps/) is very descriptive for how to create Maps of australia in ggplot. 

```{r, eval = FALSE}
install.packages("ozmaps")
```

```{r, eval = TRUE}
library(ozmaps)

#map of Australia
ozmap(x = "country")
```

<br/>  


### ozdates

The goal of ozdates is to provide historical data of important Australian dates to help with data analysis and time series modelling. The [README](https://deanmarchiori.github.io/ozdates/) is on Github. 
```{r, eval=FALSE}
devtools::install_github("deanmarchiori/ozdates")
```


```{r}
library(ozdates)
library(dplyr)
library(lubridate)

# What holidays occured in New South Wales in 2018?
nsw_hols <- aus_public_holidays %>% 
  filter(jurisdiction == "NSW",
         year(date) == "2018") %>% 
  select(date, holiday_name, jurisdiction)

nsw_hols

# Are there any public holidays in the next 2 months?
any(nsw_hols$date %within% interval(ymd("2018-04-01"), ymd("2018-05-30")))
```

<br>

### Hackerspace

[Link here](https://hackerspace.govhack.org/data_sets) to various (and copious) csv datasets used in hackerspace projects. 

