
### AFL data

A data package was put together at the [OzUnconf17](https://github.com/ropenscilabs/aflinfo). 

```{r, eval = FALSE}
devtools::install_github("ropenscilabs/aflinfo")
```


```{r, eval = TRUE}
library(AFLinfo)
```

However, the fitzRoy package is a better datasource! This package is on CRAN, and accesses data from afltables.com and footywire.com. The author [produced a talk](https://www.youtube.com/watch?v=K80leRL1U3A) on using AFL data to increase the appeal or R and stats to the public. 

```{r, eval = FALSE}
install.packages("fitzRoy")
```

The readme is very informative. 

### Cricket data

This is an international cricket data package created at [Ozunconf2017](https://github.com/ropenscilabs/cricketdata). 

Details on installing the package:

```{r, eval = FALSE}
devtools::install_github("ropenscilabs/cricketdata")
```

```{r, eval = TRUE}
suppressPackageStartupMessages(library(cricketdata)) 
```

The [readme is really useful](https://github.com/ropenscilabs/cricketdata) and describes how to fetch the data from the various sources. 


