
### Ozflights

Flight data from the Bureau of Infrastructure, Transport and Regional Economics [BITRE](https://www.bitre.gov.au/publications), downloaded using the [ozflights package](https://github.com/ropenscilabs/ozflights). See the documentation at https://github.com/ropenscilabs/ozflights. 

```{r flights, warning=FALSE, message=FALSE}
#devtools::install_github("ropenscilabs/ozflights")
library(tidyverse)

passengers <- ozflights::airport_passengers()
freight <- ozflights::international_freight()
movements <- ozflights::aircraft_movements()
airports <- ozflights::airports()
distances <- ozflights::flightdistances()

passengers %>%
  filter(airport == "TOTAL AUSTRALIA") %>%
  ggplot(aes(x = year, y = count, group = domest, colour = domest)) +
  geom_line() + facet_wrap(~type) + theme_minimal() +
  ggtitle("Inbound and outbound flight passengers in Australia")

movements %>%
  filter(airport == "TOTAL AUSTRALIA") %>%
  ggplot(aes(x = year, y = count, group = domest, colour = domest)) +
  geom_line() + facet_wrap(~type) + theme_minimal() +
  ggtitle("Flight passenger movements in Australia")

```


### Ozroaddeaths

Ozunconf18 produced a package to easily obtain this data (and did some cleaning). https://github.com/ropenscilabs/ozroaddeaths
```{r roaddeaths, warning=FALSE, message=FALSE}
library(tidyverse)

crashes <- ozroaddeaths::oz_road_fatal_crash() # NOT WORKING
fatalities <- ozroaddeaths::oz_road_fatalities()
```



### Vehicle use in Australia 2018

Data about motor vehicle use in Australia from the Australian Bureau of Statistics [link](https://www.abs.gov.au/ausstats/Subscriber.nsf/LookupAttach/9208.0Data+Cubes-20.03.191/$File/92080do001_1202201810.xls).
